Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-10-15 paper/paper.Rmd
move Alex to last place

---
documentclass: jss
author:
  - name: Patrick Schratz
    affiliation: 'Friedrich Schiller University Jena'
    # affiliaton2: 'Ludwig-Maximilians-University Munich'
    # use this syntax to add text on several lines
    # must use German name, see https://www.lmu.de/de/die-lmu/struktur/zentrale-universitaetsverwaltung/kommunikation-und-presse/lmu-brand-guide/content-style-guide/index.html
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{patrick.schratz@uni-jena.de}
  - name: Alexander Brenning
    affiliation: 'Friedrich Schiller University Jena \AND'
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{alexander.brenning@uni-jena.de}
  - name: Marc Becker
    affiliation: 'Ludwig-Maximilians-Universität München'
    address: |
      | Department of Statistics
      | Statistical Learning and Data Science group
    # To add another line, use \AND at the end of the previous one as above
  - name: Michel Lang
    affiliation: TU Dortmund University
    address: |
      | Faculty of Statistics
title:
  formatted: "\\pkg{mlr3spatiotempcv}: Spatiotemporal resampling methods for machine learning in R with \\pkg{mlr3}"
  # If you use tex in the formatted title, also supply version without
  plain:     "mlr3spatiotempcv: spatiotemporal resampling methods for machine learning in R with mlr3"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Spatial and spatiotemporal machine-learning models require a suitable framework for their model assessment, model selection, and hyperparameter tuning, in order to avoid error estimation bias and over-fitting.
  This contribution reviews the state-of-the-art in spatial and spatiotemporal CV, and introduces the R package [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) as an extension package of the machine-learning framework [mlr3](https://mlr3.mlr-org.com).
  Currently various R packages implementing different spatiotemporal partitioning strategies exist: blockCV, CAST, skmeans and sperrorest.
  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simple and common interface.
  This is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine-learning framework, which already has support for generic non-spatiotemporal resampling methods such as random partitioning.
  One advantage is the use of a consistent nomenclature in an overarching machine-learning toolkit instead of a varying package-specific syntax, making it easier for users to choose from a variety of spatiotemporal resampling methods.
  This package avoids giving recommendations which method to use in practice as this decision depends on the predictive task at hand, the autocorrelation within the data, and the spatial structure of the sampling design or geographic objects being studied.
keywords:
  formatted: [cross-validation, predictive performance, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [cross-validation, predictive performance, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
  \usepackage{scrextend}
  \usepackage{tablefootnote}
  \newcommand{\specialcell}[2][l]{%
    \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
    includes:
      in_header: header.tex
---

>>>>

---
documentclass: jss
author:
  - name: Patrick Schratz
    affiliation: 'Friedrich Schiller University Jena'
    # affiliaton2: 'Ludwig-Maximilians-University Munich'
    # use this syntax to add text on several lines
    # must use German name, see https://www.lmu.de/de/die-lmu/struktur/zentrale-universitaetsverwaltung/kommunikation-und-presse/lmu-brand-guide/content-style-guide/index.html
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{patrick.schratz@uni-jena.de}
  - name: Marc Becker
    affiliation: 'Ludwig-Maximilians-Universität München \AND'
    address: |
      | Department of Statistics
      | Statistical Learning and Data Science group
    # To add another line, use \AND at the end of the previous one as above
  - name: Michel Lang
    affiliation: TU Dortmund University
    address: |
      | Faculty of Statistics
  - name: Alexander Brenning
    affiliation: 'Friedrich Schiller University Jena'
    address: |
      | Department of Geography
      | Geographic Information Science group
    email: \email{alexander.brenning@uni-jena.de}
title:
  formatted: "\\pkg{mlr3spatiotempcv}: Spatiotemporal resampling methods for machine learning in R with \\pkg{mlr3}"
  # If you use tex in the formatted title, also supply version without
  plain:     "mlr3spatiotempcv: spatiotemporal resampling methods for machine learning in R with mlr3"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Spatial and spatiotemporal machine-learning models require a suitable framework for their model assessment, model selection, and hyperparameter tuning, in order to avoid error estimation bias and over-fitting.
  This contribution reviews the state-of-the-art in spatial and spatiotemporal CV, and introduces the R package [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) as an extension package of the machine-learning framework [mlr3](https://mlr3.mlr-org.com).
  Currently various R packages implementing different spatiotemporal partitioning strategies exist: blockCV, CAST, skmeans and sperrorest.
  The goal of [mlr3spatiotempcv](https://mlr3spatiotempcv.mlr-org.com) is to gather the available spatiotemporal resampling methods in R and make them available to users through a simple and common interface.
  This is made possible by integrating the package directly into the [mlr3](https://mlr3.mlr-org.com) machine-learning framework, which already has support for generic non-spatiotemporal resampling methods such as random partitioning.
  One advantage is the use of a consistent nomenclature in an overarching machine-learning toolkit instead of a varying package-specific syntax, making it easier for users to choose from a variety of spatiotemporal resampling methods.
  This package avoids giving recommendations which method to use in practice as this decision depends on the predictive task at hand, the autocorrelation within the data, and the spatial structure of the sampling design or geographic objects being studied.
keywords:
  formatted: [cross-validation, predictive performance, machine learning, autocorrelation, spatial, temporal, "\\proglang{R}"]
  plain:     [cross-validation, predictive performance, autocorrelation, spatial, temporal, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{amssymb}
  \usepackage{booktabs}
  \usepackage{longtable}
  \usepackage{adjustbox}
  \usepackage{multirow}
  \usepackage{tabularx}
  \usepackage{placeins}
  \usepackage{scrextend}
  \usepackage{tablefootnote}
  \newcommand{\specialcell}[2][l]{%
    \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
tables: true
bibliography: paper.bib
output:
  bookdown::pdf_book:
    base_format: rticles::jss_article
    includes:
      in_header: header.tex
---
